The host galaxy of the short GRB~111117A at $z = 2.211$\thanks{Based on observations collected at ESO/VLT under programme 088.A-0051 and 091.D-0904, at TNG under programme A24TAC\_38, at Gemini North under programme GN-2011B-Q-10 and GTC under programme GTC43-11B.}

### 2017-11-24 referee_reply.txt

--"Both of these
authors report z-band photometry that is brighter by 0.8 mag to 1.0 mag compared
to our value" -- Are the authors comparing their Gemini z-band to z-band
measurements in the other papers? Or the VLT measurement to the measurements in
other papers? If the former, the previous values are actually brighter by
1.2-1.4 mag; if the latter, the values are discrepant by 0.7 to 0.9 mag. I could
not figure out the quoted values of 0.8 to 1.0 mag.
JS: We have changed this to ~ 1 mag. Both our z-band measurements are fainter than the z-band magnitudes reported by other authors.

Fig. 3: best-fist --> best-fit
JS: Done

Section 3: --"The sub-samples comrprise of 333 long, 19 short..." - the papers
where the data came from should be cited. 
These references were in the caption, but have now been repeated in the text. 
--"had a luminosity of 44.95" --> should appear as a power of 10 and with units 
JS: This has been updated.

--"GRB 111117A has a 96% probability of being a sGRB" 
JS: Done

-- The terms sGRB and non-collapsar seem to be used interchangeably here. From the burst properties it certainly
seems like a sGRB. To be more accurate I would say "non-collapsar"
JS: We have removed the usage of non-collapsar and stuck with sGRB.

--"... it occurred when the universe was younger by 1.8 Gyr compared to any
other non-collapsar GRB ever detected"
JS: Done

-- again, how do you find non-collapsar? There is no way to know for certain and
the Bromberg+ 2013 method has been proven unreliable from host galaxy
properties. If you do want to rely on Bromberg+ 2013, what percent probability
do you consider as a "non-collapsar GRB"?
JS: We have stated a f_NC > 50 per cent requirement of the Bromberg classification to consider a given burst short.

--"This number is 3.2 Gyr for the next-highest spectroscopic redshift" - This
sentence needs a citation and would be helpful to state what burst this is
JS: We have expanded this entire section a bit to be more complete.

--Even though the offset does not change much, it is worth recalculating in this
paper for completeness.
JS: Done

--"Along with the absence of dust" -- This is not yet proven in this paper. I
suggest revising to "If the assumption of no dust is correct..."
JS: This has been changed to "low dust content"

--The scenario in which the density of material is high to explain the high NH
would imply a bright afterglow, although would appear faint at z=2.211. Are the
afterglow limits still consistent with a high-density environment at z=2.211?
The X-ray afterglow is not strongly dependent of the density and because of the optical
darkness, dust extinction locally to the GRB can accomodate a large brightness
interval. We have mentioned this in text.

Fig. 4: A comparison of the light curve for GRB 111117A to the identical figure
in Margutti+ (their Fig 6) looks like the luminosity does not change, even
though it should be significantly higher given the revised redshift. In fact,
the Margutti+ light curve exceeds 10^48 erg s^-1 near the start, while the light
curve in Fig. 4 does not. Is the luminosity calculated correctly, or are they in
different energy bands? -Does this include the Chandra data as well? If so, it
would be good to include that in the caption.

Margutti didn't use the light curve from the Swift Burst Analyser. Her early light curve is ~0.18 dex brighter.
The shape is also a bit different. k-correction: Margutti fixed the photon index
to 2.2. The Burst Analyser provides estimates of the photon index for each
observation. At the time of the first observation, the Burst Analyser gives a
photon index of 0.93. The k-correction for a power-law shaped spectrum is:
(1+z)^(Gamma-2). The difference in these parameters corresponds to a difference
in the k-correction of 0.63 dex. The different distances gives a luminosity
difference of 0.58 dex (differences in the cosmology are taken into account).

All in all, logL(us) - logL(Margutti) = (0.58 - 0.18 - 0.63) dex = -0.23 dex.

Comparing her plot with ours gives difference of ~-0.2 dex, which is identical to the expected difference.

Fig. 5: What are the lines and what is the red curve that appear on the top and
side of the plot? 
JS: The caption has been expanded to better explain the different
components.

Section 5: -"this places a hard upper limit on the initial
separation..." - Is there a citation for the equation used to calculate this?
JS: The equation is in the Postnov reference. The actual calculation is included in
the online repository, with reference to the exact equation.

-This may be outside the scope of this work, but how does
the initial separation change under different mass assumptions (unequal mass
binary, or more/less massive binary)? 
JS: We have included the calculation for different mass assumptions and changed the text accordingly.

-The authors should note that this
discussion assumes that GRB 111117A did not form dynamically in a globular
cluster as suggested by some works (e.g., Lee+ 2010; Church+ 2011)
JS: We do not assume anything about the formation channel, only that the neutron
star binary was already in place at the beginning of the universe. We have for
completeness mentioned the possible dynamical origin of neutron star binaries.

Section 6: -"The high NH is difficult to reconcile with the large projected host
offset" - How large is the offset at z=2.211? -"for between 43 and 71 percent of
sGRB hosts" -- should be revised to "sGRBs with known or well-characterized
hosts"
JS: We have changed the wording.
-------------------
